\documentclass{article}
\usepackage{geometry}
\geometry{margin=2.5cm}

\begin{document}

\begin{center}
  {\Large\bfseries Consulting Services Agreement}
\end{center}

\vspace{0.3cm}

This Agreement is entered into as of \textbf{April 25, 2026} (``Effective Date'') between:

\vspace{0.2cm}

\noindent
\textbf{Client:} Acme Corporation, a Delaware corporation with principal offices at 100 Market Street, San Francisco, CA 94103.

\vspace{0.2cm}

\noindent
\textbf{Consultant:} Jane Doe, an independent contractor residing at 42 Elm Street, Boston, MA 02108.

\vspace{0.3cm}

\subsection*{1. Services}
Consultant agrees to provide software architecture consulting services as described in Exhibit A, including code review, design reviews, and team mentoring.

\subsection*{2. Compensation}
Client shall pay Consultant \$250 per hour for services rendered, billed monthly in arrears. Payment terms are net 30 days from invoice date.

\subsection*{3. Term and Termination}
This Agreement shall commence on the Effective Date and continue for twelve (12) months unless terminated earlier. Either party may terminate with thirty (30) days written notice.

\subsection*{4. Confidentiality}
Consultant acknowledges receipt of confidential information and agrees to maintain confidentiality for a period of three (3) years from termination.

\subsection*{5. Independent Contractor}
The parties acknowledge that Consultant is an independent contractor and not an employee of Client.

\subsection*{6. Governing Law}
This Agreement shall be governed by the laws of the State of California.

\vspace{0.5cm}

\noindent
IN WITNESS WHEREOF, the parties have executed this Agreement as of the Effective Date.

\vspace{0.8cm}

\noindent
\rule{5cm}{0.4pt} \hfill \rule{5cm}{0.4pt} \\
Jane Doe (Consultant) \hfill Authorised Signer (Acme Corporation)

\end{document}
