\documentclass{article}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=1in}

\begin{document}

\begin{center}
  {\Large\bfseries CS 343: Advanced Algorithms} \\
  Fall 2026 --- MWF 10:00--10:50 --- Room Hubbard 310
\end{center}

\vspace{0.3cm}

\noindent
\textbf{Instructor:} Prof. Anna Park (a.park@example.edu) \\
\textbf{Office hours:} Tu/Th 2--4 pm, or by appointment \\
\textbf{TA:} Sam Wu (s.wu@example.edu) \\
\textbf{Prerequisites:} CS 241 or instructor consent

\subsection*{Course description}
This course covers randomised, approximation, and online algorithms with emphasis on matching theory, online learning, and streaming.

\subsection*{Learning outcomes}
By the end of this course, students will be able to:
\begin{itemize}[noitemsep]
  \item Apply the probabilistic method to combinatorial problems.
  \item Analyse approximation ratios for NP-hard problems.
  \item Design and analyse streaming algorithms.
  \item Derive regret bounds for online learning algorithms.
\end{itemize}

\subsection*{Grading}
\begin{itemize}[noitemsep]
  \item Problem sets (40\%)
  \item Midterm (25\%)
  \item Final project (25\%)
  \item Participation (10\%)
\end{itemize}

\subsection*{Topics (by week)}
\begin{enumerate}[noitemsep]
  \item Probabilistic method
  \item Randomised algorithms I: graph algorithms
  \item Randomised algorithms II: hashing and Bloom filters
  \item Approximation I: greedy and LP rounding
  \item Approximation II: primal-dual
  \item Midterm
  \item Streaming: count-min sketch and beyond
  \item Online learning: multiplicative weights
  \item Online learning: online convex optimisation
  \item Online matching: RANKING and beyond
  \item Submodular optimisation
  \item Project presentations
\end{enumerate}

\subsection*{Academic integrity}
Collaboration on problem sets is encouraged at the level of ideas; write-ups must be your own. Use of AI assistants must be disclosed.

\end{document}
