\documentclass[11pt]{article}
\usepackage{geometry}
\usepackage{enumitem}
\geometry{margin=1in}

\title{Research Grant Proposal: Scalable Graph Learning}
\author{Principal Investigator: Dr Lee}
\date{Funding Year 2026--2028}

\begin{document}
\maketitle

\section{Specific Aims}
We propose a three-year program to develop scalable graph neural network methods for trillion-edge graphs encountered in citation networks and web corpora.

\textbf{Aim 1:} Develop a subgraph sampling method with provable approximation guarantees.

\textbf{Aim 2:} Build and release an open-source framework for large-graph training.

\textbf{Aim 3:} Apply the methods to three application domains: recommendation, fraud detection, and scientific knowledge graphs.

\section{Significance and Innovation}
Current graph learning methods do not scale beyond a few billion edges without compromising accuracy or requiring prohibitive compute. This program addresses that gap.

\section{Research Plan}

\subsection{Year 1: Theoretical foundations}
We will derive approximation bounds for our sampling method and validate empirically on medium-scale graphs.

\subsection{Year 2: Framework implementation}
We will implement the framework on top of PyTorch Geometric and open-source it.

\subsection{Year 3: Applications}
We will apply the framework to citation, commerce, and biomedical graphs in collaboration with industry partners.

\section{Timeline and Deliverables}
\begin{itemize}
  \item Y1 Q2: theoretical paper submitted
  \item Y2 Q1: framework public beta
  \item Y2 Q4: framework v1.0 release
  \item Y3 Q3: three application papers submitted
\end{itemize}

\section{Budget}
Total requested: \$750{,}000 over three years, covering two PhD students, compute, and travel.

\end{document}
