\documentclass{article}
\usepackage{enumitem}

\begin{document}

\section*{Weekly Engineering Sync --- April 22, 2026}

\textbf{Attendees:} Alice, Bob, Carol, Diana, Erik \\
\textbf{Absent:} Frank (PTO) \\
\textbf{Note-taker:} Carol

\subsection*{Agenda}
\begin{enumerate}[noitemsep]
  \item Review last week's action items
  \item Sprint planning
  \item Deployment pipeline update
  \item Open floor
\end{enumerate}

\subsection*{Previous action items}
\begin{itemize}[noitemsep]
  \item \textbf{[Done]} Alice: Deploy staging environment for the new auth service.
  \item \textbf{[In progress]} Bob: Draft API spec for the billing module.
  \item \textbf{[Not started]} Diana: Runbook for on-call rotation.
\end{itemize}

\subsection*{Sprint planning}
The team committed to 34 story points for the coming sprint, up from 28 the previous sprint. The main initiatives are the auth migration (Alice, Erik) and billing module (Bob).

\subsection*{Deployment pipeline update}
Diana reported that the new deployment pipeline reduces average deploy time from 18 minutes to 6 minutes. Full rollout to all services is planned for next sprint.

\subsection*{New action items}
\begin{itemize}[noitemsep]
  \item Alice: Complete auth migration by end of sprint.
  \item Bob: Submit billing API spec for review.
  \item Carol: Schedule next retro.
  \item Diana: Lead migration to new deployment pipeline.
  \item Erik: Pair with Alice on auth token validation.
\end{itemize}

\subsection*{Next meeting}
Monday April 29, 10am, Room 3B.

\end{document}
